# Assessment data

## Introduction

Below you will find a series of datasets. You can choose to use these for the summative assessment. Alternatively, you can contact me with a suggestion of a dataset and a relevant research question. See the [Course Overview](https://cjbarrie.github.io/CTA-ED/course-overview.html) page for full details of the assessment.

## @osnabrugge_playing_2021 data

We can access data from @osnabrugge_playing_2021 [here](https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/QDTLYV)

To prepare these data, we can use the same code as used by the original authors:

```{r, message = FALSE, warning=FALSE}
library("ggplot2")
library("plyr")
library("gdata")
library("stringr")
library("data.table")
library("kableExtra")
library("tidyverse")
```


```{r, eval= FALSE}
## Prep Osnabrugge et al. - after downloading the dataset (see instructions above), check where you have stored in on your computer and include the path to the data in the code below.
# I have given you the example with the path on my own computer, but you will need to change it.
data = fread("User/marionlieutaud/document/data/osnabrugge_uk_data.csv", encoding="UTF-8")


data$date = as.Date(data$date)


#Table 2: Examples: Emotive and neutral speeches
example1 = subset(data, id_speech==854597)
example1$emotive_rhetoric
example1$text

example2 = subset(data, id_speech==778143)
example2$emotive_rhetoric
example2$text

#Create time variable
data$time= NA
data$time[data$date>=as.Date("2001-01-01") & data$date<=as.Date("2001-06-30")] = "01/1"
data$time[data$date>=as.Date("2001-07-01") & data$date<=as.Date("2001-12-31")] = "01/2"
data$time[data$date>=as.Date("2002-01-01") & data$date<=as.Date("2002-06-30")] = "02/1"
data$time[data$date>=as.Date("2002-07-01") & data$date<=as.Date("2002-12-31")] = "02/2"
data$time[data$date>=as.Date("2003-01-01") & data$date<=as.Date("2003-06-30")] = "03/1"
data$time[data$date>=as.Date("2003-07-01") & data$date<=as.Date("2003-12-31")] = "03/2"
data$time[data$date>=as.Date("2004-01-01") & data$date<=as.Date("2004-06-30")] = "04/1"
data$time[data$date>=as.Date("2004-07-01") & data$date<=as.Date("2004-12-31")] = "04/2"
data$time[data$date>=as.Date("2005-01-01") & data$date<=as.Date("2005-06-30")] = "05/1"
data$time[data$date>=as.Date("2005-07-01") & data$date<=as.Date("2005-12-31")] = "05/2"
data$time[data$date>=as.Date("2006-01-01") & data$date<=as.Date("2006-06-30")] = "06/1"
data$time[data$date>=as.Date("2006-07-01") & data$date<=as.Date("2006-12-31")] = "06/2"
data$time[data$date>=as.Date("2007-01-01") & data$date<=as.Date("2007-06-30")] = "07/1"
data$time[data$date>=as.Date("2007-07-01") & data$date<=as.Date("2007-12-31")] = "07/2"
data$time[data$date>=as.Date("2008-01-01") & data$date<=as.Date("2008-06-30")] = "08/1"
data$time[data$date>=as.Date("2008-07-01") & data$date<=as.Date("2008-12-31")] = "08/2"
data$time[data$date>=as.Date("2009-01-01") & data$date<=as.Date("2009-06-30")] = "09/1"
data$time[data$date>=as.Date("2009-07-01") & data$date<=as.Date("2009-12-31")] = "09/2"
data$time[data$date>=as.Date("2010-01-01") & data$date<=as.Date("2010-06-30")] = "10/1"
data$time[data$date>=as.Date("2010-07-01") & data$date<=as.Date("2010-12-31")] = "10/2"
data$time[data$date>=as.Date("2011-01-01") & data$date<=as.Date("2011-06-30")] = "11/1"
data$time[data$date>=as.Date("2011-07-01") & data$date<=as.Date("2011-12-31")] = "11/2"
data$time[data$date>=as.Date("2012-01-01") & data$date<=as.Date("2012-06-30")] = "12/1"
data$time[data$date>=as.Date("2012-07-01") & data$date<=as.Date("2012-12-31")] = "12/2"
data$time[data$date>=as.Date("2013-01-01") & data$date<=as.Date("2013-06-30")] = "13/1"
data$time[data$date>=as.Date("2013-07-01") & data$date<=as.Date("2013-12-31")] = "13/2"
data$time[data$date>=as.Date("2014-01-01") & data$date<=as.Date("2014-06-30")] = "14/1"
data$time[data$date>=as.Date("2014-07-01") & data$date<=as.Date("2014-12-31")] = "14/2"
data$time[data$date>=as.Date("2015-01-01") & data$date<=as.Date("2015-06-30")] = "15/1"
data$time[data$date>=as.Date("2015-07-01") & data$date<=as.Date("2015-12-31")] = "15/2"
data$time[data$date>=as.Date("2016-01-01") & data$date<=as.Date("2016-06-30")] = "16/1"
data$time[data$date>=as.Date("2016-07-01") & data$date<=as.Date("2016-12-31")] = "16/2"
data$time[data$date>=as.Date("2017-01-01") & data$date<=as.Date("2017-06-30")] = "17/1"
data$time[data$date>=as.Date("2017-07-01") & data$date<=as.Date("2017-12-31")] = "17/2"
data$time[data$date>=as.Date("2018-01-01") & data$date<=as.Date("2018-06-30")] = "18/1"
data$time[data$date>=as.Date("2018-07-01") & data$date<=as.Date("2018-12-31")] = "18/2"
data$time[data$date>=as.Date("2019-01-01") & data$date<=as.Date("2019-06-30")] = "19/1"
data$time[data$date>=as.Date("2019-07-01") & data$date<=as.Date("2019-12-31")] = "19/2"

data$time2 = data$time
data$time2 = str_replace(data$time2, "/", "_")

data$stage = 0
data$stage[data$m_questions==1]= 1
data$stage[data$u_questions==1]= 2
data$stage[data$queen_debate_others==1]= 3
data$stage[data$queen_debate_day1==1]= 4
data$stage[data$pm_questions==1]= 5

```

Below, I display a sample of these data.

```{r, echo=FALSE}

data <- readRDS("data/assessment/osnabrugge_samp.rds")

```

```{r, echo=F}

data <- data[1:3,]

data %>%
  select(id_speech, text, last_name, first_name, date, government, female, age) %>%
  kable() %>%
  kable_styling(bootstrap_options = "striped")
```

If the full dataset is too large for your machines, you can easily take a sample of it with:

```{r, eval=F}

data_samp <- data %>%
  sample_n(10000)

```

## Twitter Transparency data

Select a dataset/datasets of interest from the Twitter Transparency archive [here](https://transparency.twitter.com/en/reports/information-operations.html). These are datasets that have been flagged for "information operations" activity; that is, activity designed to distort, often through automated messaging, the information landscape to the benefit of a given entity (normally a government).

The datasets are all listed and downloadable in ".csv" format if you scroll down to "03. Download Archive." Here, you will just be asked to enter your email address as agreement to Terms of Use.

## @waller2021

You can download embeddings and online community scores used in this article the Github repo linked [here](https://github.com/CSSLab/social-dimensions).

To get the community embeddings data in usable format we can do:

```{r, eval = F}

embeddings <- read.table("https://raw.githubusercontent.com/CSSLab/social-dimensions/main/data/embedding-vectors.tsv")

embeddings_metadata <- data.table:::fread("https://raw.githubusercontent.com/CSSLab/social-dimensions/main/data/embedding-metadata.tsv")

embeddings_scores <- read.csv("https://raw.githubusercontent.com/CSSLab/social-dimensions/main/data/scores.csv")

                    
```

Then to add in information on what each vector of dimensions 150 (i.e., here: columns), we can add in the community information to the embeddings with:

```{r, eval = F}
communities <- embeddings_metadata$community

rownames(embeddings) <- communities
```

## R Markdown

You can access a template R Markdown response for your code from the Github repo for this book by clicking this [link](https://raw.githubusercontent.com/cjbarrie/CTA-ED/main/data/assessment/CTA_example.Rmd?raw=true) and download the word document it outputs by clicking this [link](https://github.com/cjbarrie/CTA-ED/blob/main/data/assessment/CTA_example.docx?raw=true).

Though you **should submit the R markdown output in word** you can also see what it looks like when generated as html [here](https://raw.githack.com/cjbarrie/CTA-ED/main/data/assessment/CTA_example.html).

## Marking criteria

A1 (90-100%) and-A2 (80-89%)

An exceptional assignment. The discussion and analysis is not only sophisticated but innovative. It critically engages with diverse literatures – substantive and methodological – and it deploys computational text analysis methods powerfully to craft an original and academically robust argument. The work may be of a standard that would be publishable in peer-reviewed academic journals (particularly for A1).  

-	Argument: highly-focused and academically convincing argument that fully addresses the question/prompt. This argument is exceptionally sophisticated, conceptually, theoretically and methodologically and is rigorously supported and elaborated through the empirical analysis. The empirical material and analysis go beyond the illustrative to generate an exceptionally insightful academic analysis. The argument is informed by advanced engagement with relevant academic literature, and builds logically towards authoritative conclusions. Overall, the quality of the argument demonstrates an advanced capacity to critically engage with computational methods and relevant existing literatures and convincingly present evidence so as to develop and define new and abstract problems and issues and so advance understanding in the area of enquiry.
-	Comprehension: demonstrates a precise, correct and appropriately detailed understanding of key concepts, methods and evidence, grounded in an exceptionally insightful reading of relevant literature. The literature is synthesised in illuminating and creative ways to support an academic argument that emerges from but goes beyond that literature. 
-	Writing: prose is precisely and clearly understood by the reader. This prose may convey a distinctive academic “voice”, but always supports persuasive communication in a manner appropriate to the task. The text is logically structured and organised throughout such that the reader can easily follow the progression of argument. Prose will be (almost) wholly free of mistakes of spelling and grammar, permitting idiosyncrasies of expression providing the substance of the argument is clear. Sources should be referenced with exceptional thoroughness and precision, according to accepted academic formats and standards. 
-	Method: The text analysis method(s) deployed is/are compellingly-justified and perfectly suited to the research question. Data preprocessing decisions are clearly explained and justified. The model is impeccably fitted; model outputs are well-presented (using impeccable visualisations and/or tables where appropriate), rigorously analysed and validated. All relevant caveats for the method(s) or material chosen are critically identified and pondered, not only in generic terms but in ways specific to the research question and empirical material.
-	Code: the code is impressively optimised and perfectly commented. It compiles cleanly to a well-formatted word output.

A3 (70-79%)

An excellent assignment. It has a sharply-focused discussion of high intellectual quality, shows very good command of the methods deployed, and maintains a sophisticated level of analysis throughout. It critically engages with a range of literature – theoretical and methodological - and moves beyond it, using the sources and empirical material correctly to creatively arrive at independent conclusions. More specifically:

-	Argument: a focussed and academically convincing academic argument that clearly responds to the assignment question/prompt. This argument is conceptually, theoretically and methodologically sophisticated and thoroughly supported and elaborated through empirical material and analysis. The argument is grounded in precise and detailed engagement with relevant academic literature (both substantive and methodological), and follows a logical progression to compelling conclusions. Overall, the quality of the argument demonstrates a capacity to work existing literatures and generate evidence to develop and define new and abstract problems and issues and so advance understanding in the area of enquiry.
-	Comprehension: demonstrates a precise, generally correct and appropriately detailed understanding of key concepts, methods and examples which is grounded in, and supported by, an insightful reading of relevant literatures. Engagement with literature and with the empirical analysis moves beyond merely summarising or providing overviews, to present creative and insightful analyses, interpretation and synthesis.
-	Writing: prose is precisely and clearly understood by the reader. This prose may convey a distinctive academic “voice”, but always supports persuasive communication in a manner appropriate to the task. The text is logically structured and organised throughout such that the reader can easily follow the progression of argument. The text is mostly free of mistakes of spelling and grammar, permitting idiosyncrasies of expression providing the substance of the argument is clearly articulated. Sources should be thoroughly and precisely attributed, in keeping with accepted academic formats and standards. 
-	Method: The text analysis method deployed is well-justified and well-suited to the research question. Data preprocessing decisions are clearly explained and justified. The model is well fitted; model outputs are well-presented (using visualisations and/or tables where appropriate), rigorously analysed and often validated. Caveats for the method(s) chosen are critically identified and pondered, not only in generic terms but in ways specific to the research question and empirical material.
-	Code: the code is optimised and well-commented. It compiles cleanly to a well-formatted word output.

B- (60-63%), B (64-66%) and B+ (67-69%)

A good (B- to B) to very good (B to B+) assignment. It has a focussed discussion of above average intellectual quality, sound methodological reasoning and deployment, and maintains a high level of analysis in most of the assignment, albeit with shortcomings in argument and/or methods. It demonstrates thoughtful, detailed and sometime creative engagement with relevant literature – substantive and methodological - , and it deploys relevant computational methods well, with some limitations in comprehension and/or analysis. On that basis, it offers distinctive insights that go beyond simply paraphrasing others’ ideas. Assignments may fall into this grade band despite generally excellent performance when there are significant specific problems identified with aspects of the argument, comprehension, method, code or writing.

-	Argument: generally convincing and focussed academic argument that responds directly to the research question with an adequate choice of method and data, and provides insights, potentially with some limitations in reasoning or articulation. This argument is conceptually and theoretically informed and it is supported by empirical material and analysis. The empirical analysis may be used in a more illustrative fashion, rather than to elaborate or develop the argument, or may be engaged with insufficient depth to fully substantiate the arguments. Conclusions are reasonable and relate to a preceding progression of argument. Overall, the quality of the argument suggests an ambition to work with existing literatures, methods and evidence to conceptualise and define new and abstract problems and issues and so advance understanding in the area of enquiry, although this ambition may be limited or the resulting arguments may read as being somewhat speculative.  
-	Comprehension: demonstrates generally correct and fairly detailed critical understanding of key ideas, concepts and examples which is grounded in, and supported by, a reasonably insightful reading of relevant literatures – substantive and methodolofical. There may be some significant misunderstandings or gaps in engagement, some misfitting of models or misinterpretation of outputs. There is critical engagement and synthesis of literature and choice of methods in relation to the argument, though some engagement may tend towards the descriptive or lack focus. 
-	Writing: prose can be clearly understood through most of the assignment. Though containing some limitations in terms of clarity, it still conveys the academic argument in a manner appropriate to the task. The text is generally well structured and organised, though there may be some minor difficulties following the progression of argument. Mostly free of mistakes of spelling and grammar, permitting idiosyncrasies of expression providing the substance of the argument is clearly articulated. A generally high standard of referencing in keeping with accepted academic formats and standards, although there may be some errors in this respect. 
-	Method: The text analysis method deployed is justified and can address the research question. Data preprocessing decisions are explained. The model is mostly well-fitted though there may be some mistakes; model outputs are on the whole well-presented (using visualisations and/or tables where appropriate). Analysis is mostly sound and includes some validation, though there may be some mistakes, some over- or under-interpretation, i.e. the analysis may be at times too descriptive and fail to clearly draw out all the implications and conclusions from the empirical analysis. Some caveats for the method(s) chosen or the data are critically identified and pondered, but this may miss some caveats or remain quite generic in parts
-	Code: the code works and is mostly well-commented. It compiles to a mostly well-formatted word output.

C- (50-53%) C (54-56%) C+ (57-59%)

A satisfactory (C- to C) to quite good (C to C+) assignment. It has a discussion which clearly and consistently addresses the assignment question/prompt. The argument may be generic, or over-reliant on propositions not suitably developed though, and supported, by the academic literature and the empirical analysis. The assignment demonstrates reasonable levels of engagement with relevant literature – substantive and methodological -, even if the quality of engagement tends to be overly descriptive or lacking in precision and detail. Methods learnt in the course are used but are inconsistently deployed and interpreted. Assignments may fall into this grade band despite stronger performance on other general criteria when there are significant specific problems such as not addressing the assignment question, using inappropriate source material, overfocusing on code or analysis and falling short on interpretation, or containing frequent incorrect assertions or misunderstandings.

- Argument: the argument provides a reasonable response to the assignment question/prompt. It demonstrates some engagement with relevant conceptual, theoretical and methodological issues, although the quality of that engagement may be lacking in detail and precision. There is an effort to support the argument with empirical material and analysis, though this may lack detail and depth sufficient to convincingly substantiate or elaborate the arguments. Alternatively, the analysis may be partially disconnected from the core research question and argument. The argument is grounded in some engagement with relevant academic literature, although the range may be limited and engagement more in the form of descriptive summaries. Alternatively, propositions may be advanced that do not suitably refer to academic literature or to the empirical evidence generated, and therefore read as speculative (overinterpretation). Conclusions will be relevant but may not connect fully to the preceding argument and the analysis. Overall, the quality of the overall argument may be sound but does not suggest an ambition to conceptualise and define new and abstract problems and issues and so advance understanding in the area of enquiry.
-	Comprehension: demonstrates an adequate level of understanding of key ideas, concepts, and methods, grounded in some relevant literature – substantive and methodological. The range of reading may, however, be quite limited or contain significant amounts of irrelevant material. There is some critical engagement with respect to the literature, the choice of method and the data, but this may be lacking in the precision or detail and may tend towards the descriptive rather than interpretive. There may be some important misunderstandings or misrepresentations of key methods or ideas.
-	Writing: The prose communicates an academic argument in a manner appropriate to the task, although there may be passages that suffer from being incoherent, opaque or vague. There may be frequent minor mistakes of spelling and grammar, or the prose may be idiosyncratic to a degree that inhibits the clear articulation of the argument. The assignment will have a discernible structure, but may suffer from poor organisation of the material or a confusing progression between topics. Sources will be appropriately referenced, although there may be some minor errors and omissions, or the format may not be wholly consistent with accepted academic formats and standards.  
- Method: The text analysis method deployed is only partially justified and a moderate fit to the research question. Data preprocessing decisions are partially explained. Some analytical models are adequately fitted, or deployed in part, though there are some mistakes; some of the model outputs are adequately presented (using visualisations and/or tables), though some may be irrelevant, redundant or poorly presented. The analysis is sound in part and there is some effort to validate findings, though there are some mistakes, some over- or under-interpretation, i.e. the analysis may be at times too descriptive and fail to draw out all the implications and conclusions from the empirical analysis. The assignment hints at a critical assessment of the method(s) chosen or the data but this lacks in depth or specificity.
-	Code: the code runs and compiles to word but the knitted document and the code are imperfectly formatted, the code is sporadically commented and clunky.

D- (40-43%) D (44-46%) D+ (47-49%)

A barely passable (D- to D) to passable (D to D+) assignment. It has a discussion which provides a suitable response to the question/prompt, albeit in a manner that may be unconvincing to a significant degree. There is some demonstration of engagement with relevant literature – substantive and methodological - , though of limited quality. The assignment uses methods learned in the course and provides an empirical analysis of material that is however moderately convincing. Assignments may fall into this grade band despite stronger performance on the main general criteria when there are significant specific problems such as not addressing the assignment question, using inappropriate material, mis-fitting or mis-interpreting models, or containing frequent incorrect assertions of misunderstandings.

-	Argument: The assignment provides an argument that may be read as responding to the assignment question/prompt. The quality of this argument demonstrates some very limited or speculative engagement with conceptual, theoretical and methodological issues suggested. This argument is supported by, and elaborated through, some empirical analysis. However, it may be that the analysis is not wholly effective as a means of developing the argument. Alternatively, the empirical evidence may lack clear relevance to the argument. The argument will be developed in some engagement with relevant academic literature, although the range of literature may be very limited and this engagement may be more in the form of summaries or tend towards the broadly and vaguely descriptive. Alternatively, some propositions may be advanced that do not at all refer to academic literatures or the empirical evidence generated and therefore read as wholly speculative.  
-	Comprehension: demonstrates some understanding of key ideas, concepts, and methods, grounded in, and supported by, a limited reading of relevant literature – substantive and methodological. The understanding may, however, be very approximate, vague and occasionally uncertain, with major misunderstandings or misrepresentations. Alternatively, the assignment may over-rely on empirical evidence that are either not particularly relevant to the topic or of a kind that would not support a credible academic argument. 
- Writing: The assignment is written in prose of a quality that makes it difficult for the reader to discern and appreciate the substance of the argument and discussion. This may because of significant grammatical errors, or prose idiosyncratic to a degree that makes arguments inaccessible. Alternatively, the prose style adopted may be wholly inappropriate to the task. The assignment may lack a clear structure or systematic organisation. Sources should be appropriately referenced, although there may be significant errors and omissions, or major inconsistencies with accepted academic formats and standards. 
- Method: The text analysis method deployed is improperly justified and a moderate fit to the research question. Data preprocessing decisions are barely explained and not wholly adequate. Some analytical models are deployed or deployed in part, but often inadequately; few of the model outputs are adequately presented (using visualisations and/or tables), some may be irrelevant, redundant or poorly presented. There is no effort to validate findings. The analysis includes recurring and important mistakes, over- or under-interpretation, i.e. the analysis may erroneous, entirely too descriptive and failing to draw out all the implications and conclusions from the empirical analysis, or wholly speculative. The assignment lacks critical assessment of the method(s) chosen or the.
- Code: Most of the code runs though it may not adequately compiles to word. Where it compiles, the knitted document and the code are imperfectly formatted, the code is not commented, clunky and not functional or erroneous in parts.


E (30-39%)

A failing assignment. It is distinguished by a discussion which is at best only vaguely related to the assignment question/prompt or, alternatively, is exceptionally underdeveloped (and may fall well short of the word limit). The assignment may also be seriously lacking in any engagement with relevant academic literature and show little or no evidence of an informed understanding of key concepts and theories. It fails to deploy methods learnt in the course or fails to do so adequately. It could be that some ideas and propositions in this assignment have potential academic merit, which would be realised with their being better developed, more methodological understanding, and in reference to the relevant literature.

- Argument: The assignment provides an argument that may be fragmentary, incoherent but nonetheless may generously be read as a response to the assignment question/prompt. This argument may be exceptionally limited or speculative suggesting only the most rudimentary familiarity with the conceptual, theoretical and methodological issues suggested by the assignment question/prompt. Some empirical analysis may be provided but their relevance to the argument may be unclear, they may be profoundly lacking in detail and substance, or, alternatively, they elaborated in considerable descriptive detail (and so have some value) but are not clearly pertinent to the assignment question/prompt. The argument assignment may allude to academic literature, but the range of literature may be very limited and the discussion of that literature may be vague, greatly lacking in substance and demonstrating little familiarity with that literature. 

- Comprehension: The quality of the argument in this assignment may demonstrate a broad and vague familiarity with key ideas, concepts and methods which alludes to a body of academic literature, but there may lack in any suggestion that this familiarity is grounded in, and supported by, a reading of the relevant literature. By extension, discussions of this literature may read as exceptionally imprecise and occasionally wholly inaccurate. Alternatively, the assignment may wholly rely on sources that are either not relevant to the topic or may be of kind that would not support a credible academic argument and may be of dubious or suspect quality; finally, it may be that the assignment is entirely focused on uninterpreted and unjustified analysis.

- Writing: The assignment is written in prose of a quality that renders it very difficult for the reader to discern and appreciate the substance of the argument and discussion. This may because there is a profound density of quite fundamental mistakes of grammar that make it very difficult to appreciate points and follow lines of argument, or that the prose is idiosyncratic to a degree that renders these points and lines of argument obscure and inaccessible. Alternatively, the prose style adopted may be wholly inappropriate to the task. The text may be wholly, or almost wholly, lacking in the appropriate attribution of sources. Likewise, the reference list may be exceptionally partial, carelessly presented or missing altogether. 

- Method: The text analysis method chosen is either not deployed, wrongly deployed or a wrong choice for the research question. Data preprocessing decisions are not explained and/or wholly inadequate. There are barely any model outputs and they are in the main irrelevant, redundant or poorly presented. The analysis is dominated by recurring and important mistakes, over- or under-interpretation, i.e. the core of the analysis may be erroneous, entirely too descriptive and failing to draw out all the implications and conclusions from the empirical analysis, or wholly speculative. There is no effort to validate findings. The assignment lacks critical assessment of the method(s) chosen or data.

- Code: The code does not run adequately and may not compile to word. It is messy, not commented, clunky and includes many errors of malfunctions.

F (20-29%)

An assignment that is either not at all relevant to the assignment question/prompt, or is almost wholly lacking in any academically-informed knowledge of the subject, with little or no awareness of the relevant issues, methods or literature. It may be exceptionally short, fragmentary and written carelessly in a manner that makes any argument quite profoundly confusing and intelligible. Although there may be some suggestion of a familiarity with the existence of the methods and the academic literature on the subject, there may be no reference made to that literature and, correspondingly, no sources cited in the text of that assignment. It may not deploy any method covered in the course or fail to analyse the outputs altogether. 

G (10-19%)

An assignment that falls far short of a passable level by some combination of short length, complete irrelevance, profound lack of intelligibility, and no suggestion of an acquaintance with academic literatures or concepts. It fails to provide any empirical evidence for a research question using the methods introduced in the course.

H (0-9%)

An assignment utterly lacking in any academic merit which usually conveys no sense that the course has been followed or of the basic skills of assignment-writing.


